A hierarchical failure-time model for observational data exhibiting infant-mortality and wearout failure modes

### 2017-11-06 paper/aosgflp.tex
Small edit to abstract

In this paper we present a method for joint estimation of multiple lifetime distributions based on the Generalized Limited Failure Population (GLFP) model. This 5-parameter model for lifetime data accommodates lifetime distributions with multiple failure modes:  early failures due to ``infant mortality'' and failures due to wearout. We fit the GLFP model using a hierarchical modeling approach.  Borrowing strength across populations, our method enables estimation with uncertainty of lifetime distributions even in cases where the number of model parameters is larger than the number of observed failures.  Moreover, using our Bayesian method, comparison of different product brands is straightforward because estimation of arbitrary functionals are easily computable using draws from the joint posterior distribution of the model parameters. Potential applications include assessment and comparison of reliability to inform purchasing decisions.

>>>>

In this paper we present a method for joint estimation of multiple lifetime distributions based on the Generalized Limited Failure Population (GLFP) model. This 5-parameter model for lifetime data accommodates lifetime distributions with multiple failure modes:  early failures due to ``infant mortality'' and failures due to wearout. We fit the GLFP model using a hierarchical modeling approach.  Borrowing strength across populations, our method enables estimation with uncertainty of lifetime distributions even in cases where the number of model parameters is larger than the number of observed failures.  Moreover, using our Bayesian method, comparison of different product brands is straightforward because estimation of arbitrary functionals is easy using draws from the joint posterior distribution of the model parameters. Potential applications include assessment and comparison of reliability to inform purchasing decisions.
